### 2014-11-13 tex/bisimulation.tex
Minor cuts

The inspiration for $\rsym$ came from a desire to create
a new way to initialize heap objects that avoided initializing heaps
that traverse the same control flow paths. The thought was to group together heaps
into equivalence classes: all the heaps that followed the same control
flow path to a given point of execution would be in the same
equivalence class at that point of execution. An equivalence class
splits at branches, where the program actually differentiates heaps.

The proof only reasons about well-formed states, which have
deterministic, type-consistent heaps, and feasible environments, expressions, and
continuations. Well-formed states always have successors unless at the end of a 
program execution. It is trivial to show that the set of well-formed states is closed
under the transition relation.

>>>>

The inspiration for $\rsym$ came from a desire to create
a new way to initialize heap objects that avoided initializing heaps
that traverse the same control flow paths. The proof only reasons about well-formed states, which have
deterministic, type-consistent heaps, and feasible environments, expressions, and
continuations. Well-formed states always have successors unless at the end of a 
program execution. It is trivial to show that the set of well-formed states is closed
under the transition relation.

### 2014-11-13 tex/precise.tex
Minor cuts

\section{Generating Summary Heaps}
\label{sec:precise}
In this section we present the summary heap algorithm that operates on
the bipartite graph described in the previous section.  The summary
heap algorithm initializes, updates, and partitions the heap. It only
partitions the heap at points of divergence in the control flow graph
such as field accesses or writes (execeptional control flow due to null
pointers) or comparisons of references (program control flow). There
are three sets of rewrite rules specific to the summary heap
algorithm: (i) rules to initialize symbolic references, (ii) rules to
complete field access and field write, and (iii) rules to check
equality and inequality of references. The other rules are common to
both $\rsym$ and $\rgse$. The complete set of rules are shown in the
supplemental attached with the paper.

>>>>

\section{Generating Summary Heaps}
\label{sec:precise}
The summary
heap algorithm only
partitions the heap at points of divergence in the control flow graph
such as field accesses or writes (execeptional control flow due to null
pointers) or comparisons of references (program control flow). There
are three sets of rewrite rules specific to the summary heap
algorithm: (i) rules to initialize symbolic references, (ii) rules to
complete field access and field write, and (iii) rules to check
equality and inequality of references. The other rules are common to
both $\rsym$ and $\rgse$. The complete set of rules are shown in the
supplemental attached with the paper.
